### 2018-07-16 localizations.tex
ready to submit maybe

\begin{quote}
The {\bf Coverage} localization for a failing test case $f$ in the set
of failures $F$ ranks
statements by the function $r$ (for rank) where:
%$$U = s : \forall m . \forall t \in F . c(m,t,s) = 1$$
$$C(s) = \sum_{t \in F} (\sum_{m \in R(t)} c(m,t,s))$$
%\[
$$r(s,f) = \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s)$$
%\begin{cases}
% \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s) & s \not\in U\\
%   0 & s \in U
%\end{cases}
%\]
$c(m,t,s)$ is 1 if coverage of $s$ changes for test $t$
with mutant $m$, and 0 otherwise.  $R(f)$ is the set of mutants repairing $f$.
\end{quote}

@@

\begin{quote}
The {\bf Repair} localization for a failing test case $f$ ranks
statements by the function $r$ where:
%$$dmax(m,f) = max_{t : m \in R(t)} d(t,f)$$
\[
r(m,f) = 
\begin{cases}
\frac{1}{1 + max_{t \in F: m \in R(t)} d(t,f)} & m \in R(f)\\
0 & m \not\in R(f)\\
\end{cases}
\]
%$$\text{leastfar} = m \in R(f) : \neg\exists m' : \text{far}(m',f) <
%\text{far}(m,f)$$
\end{quote}

>>>>

\begin{quote}
The {\bf Coverage} localization for a failing test case $f \in F$ ($F$
is the set of all failing test cases) ranks
statements by the function $r$ (for rank) where:
%$$U = s : \forall m . \forall t \in F . c(m,t,s) = 1$$
$$C(s) = \sum_{t \in F} (\sum_{m \in R(t)} c(m,t,s))$$
%\[
$$r(s,f) = \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s)$$
%\begin{cases}
% \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s) & s \not\in U\\
%   0 & s \in U
%\end{cases}
%\]
$c(m,t,s)$ is 1 if coverage of $s$ changes for test $t$
with mutant $m$, and 0 otherwise.  $R(f)$ is the set of mutants repairing $f$.
\end{quote}

@@

\begin{quote}
For a set $F$ of failing test cases and $m$ of mutants, 
the {\bf Repair} localization for $f \in F$, where $R(f) \in m$ is the set
of mutants repairing $f$, ranks
statements by the function $r$:
%$$dmax(m,f) = max_{t : m \in R(t)} d(t,f)$$
\[
r(f) = 
\begin{cases}
\frac{1}{1 + max_{t \in F: m \in R(t)} d(t,f)} & m \in R(f)\\
0 & m \not\in R(f)\\
\end{cases}
\]
%$$\text{leastfar} = m \in R(f) : \neg\exists m' : \text{far}(m',f) <
%\text{far}(m,f)$$
\end{quote}
